---
title: "Quarto Computations"
format: 
   html:
     df-print: paged
     # df-print: default
     # df-print: kable
     # df-print: tibble
---

This dataset contains a subset of the fuel economy data from the EPA.
Specifically, we use the `mpg` dataset from the **ggplot2** package.

```{r}
#| label: load-packages
#| echo: false

library(ggplot2)
```

The visualization below shows a positive, strong, and linear relationship between the city and highway mileage of these cars.
Additionally, mileage is higher for cars with fewer cylinders.



@fig-scatterplot shows a positive, strong, and linear relationship between the city and highway mileage of these cars.

```{r}
#| label: fig-scatterplot
#| fig-cap: "City and highway mileage for 38 popular models of cars."
#| fig-alt: "Scatterplot of city vs. highway mileage for cars, where points are colored by the number of cylinders. The plot displays a positive, linear, and strong relationship between city and highway mileage, and mileage increases as the number cylinders decreases."
#| fig-width: 6
#| fig-height: 3.5

ggplot(mpg, aes(x = hwy, y = cty, color = cyl)) +
  geom_point(alpha = 0.5, size = 2) +
  scale_color_viridis_c() +
  theme_minimal()
```




Another plot with render multiple figures.


na @fig-mpg-1 deu um resultados e na @fig-mpg-2 deu outro.


```{r}
#| label: fig-mpg
#| fig-cap: "City and highway mileage for 38 popular models of cars."
#| fig-subcap:
#|   - "Color by number of cylinders"
#|   - "Color by engine displacement, in liters"
#| layout-ncol: 2
#| fig-width: 3
#| fig-height: 3.5
#| column: body

ggplot(mpg, aes(x = hwy, y = cty, color = cyl)) +
  geom_point(alpha = 0.5, size = 2) +
  scale_color_viridis_c() +
  theme_minimal()

ggplot(mpg, aes(x = hwy, y = cty, color = displ)) +
  geom_point(alpha = 0.5, size = 2) +
  scale_color_viridis_c(option = "E") +
  theme_minimal()
```



## dataframes


Na forma inline:

There are `r nrow(mpg)` observations in our data. 


```{r}
#| echo: false

mean_cty <- round(mean(mpg$cty), 2)
mean_hwy <- round(mean(mpg$hwy), 2)
```




The average city mileage of the cars in our data is `r mean_cty` and the average highway mileage is `r mean_hwy`. 



E os dataframes podem ser printados de uma forma melhor.


```{r}
mtcars
```

